### 2018-12-09 Revision/Paper/intro.tex

In this work, we adopt an iterative strategy to reduce the computational effort
associated with active subspace computation. Moreover, we explore two approaches
for estimating the gradient of the ignition delay with respect to the uncertain
rate-controlling parameters: pre-exponent, $A_i$ and the activation energy, $E_{a,i}$,
for $i^{\text{th}}$ reaction in the H$_2$/O$_2$ mechanism \rebut{as well as
the initial conditions: $P_0$, $T_0$, and $\Phi_0$. Note that the equivalence ratio
corresponding to the initial molar ratios of $H_2$ and O$_2$ is denotes as $\Phi_0$.}
As mentioned above, the
first approach uses finite difference to estimate the gradient and is regarded as
the perturbation approach, whereas, the second approach involves a linear
regression-fit to the available set of model evaluations and is regarded as
the regression approach.

>>>>

In this work, we adopt an iterative strategy to reduce the computational effort
associated with active subspace computation. Moreover, we explore two approaches
for estimating the gradient of the ignition delay with respect to the uncertain
rate-controlling parameters: pre-exponent, $A_i$ and the activation energy, $E_{a,i}$,
for $i^{\text{th}}$ reaction in the H$_2$/O$_2$ mechanism \rebut{as well as
the initial conditions: $P_0$, $T_0$, and $\Phi_0$. Note that the equivalence ratio
corresponding to the initial molar ratios of $H_2$ and O$_2$ is denotes as $\Phi_0$.}
As mentioned above, the
first approach uses finite difference to estimate the gradient and is regarded as
the perturbation approach. On the other hand, the second approach 
follows from~\cite{Constantine:2015} and involves repeated
linear regression-fits to a subset of available model evaluations, and is 
regarded as the regression approach in this work.
